Tables

### 2020-10-27 manuscript.Rmd
draft changes

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2
csl: ./other/apa.csl
urlcolor: blue
---

@@

```

@@

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
```

@@

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

INSERT COMMUNITY DETECTION

@@

@@

More info in this [documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

>>>>

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/burd_recruiting_chapter.bib
output: bookdown::pdf_document2
csl: ./other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
---

@@

library(kableExtra)
library(tidyverse)
```

@@

@@

Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university

Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities

Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited

@@

<div id="refs"></div>

<!-- TABLES -->

@@

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-ID, -Characteristics), row.names = F, 
  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-school_id,-closeness), caption = 'ego table 3') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg.RDS')

knitr::kable(df, caption = 'ego table caption') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- FIGURES -->

\newpage

\begin{landscape}

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

\end{landscape}

### 2020-10-27 tables.Rmd
draft changes

@@

```{r}
df <- readRDS('./assets/tables/table_ego.RDS')

knitr::kable(df %>% select(-ID, -Characteristics), row.names = F) %>% kable_styling(latex_options = 'scale_down')
```

>>>>

Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode.RDS')

knitr::kable(head(df, n = 20, caption = 'ego table 3')) %>% kable_styling(latex_options = 'scale_down')
```

@@

```{r}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(df %>% select(-ID, -Characteristics), row.names = F) %>% kable_styling(latex_options = 'scale_down')
```
